\LARGE \bf {\tt underworlds}: Cascading Situation Assessment for Robots

### 2017-02-24 paper.tex
Update on Overleaf.

Difficulties however arise quickly. These different components might need
different models, at different spatial and temporal resolutions. A 3D motion
planner would typically use coarse 3D models of surrounding objects to lower the
computational load while planning, while a spatial reasoner might need on the
contrary a high-resolution model of the environment for accurate rendering when
attempting to estimate the visibility of an object. Spatial models are also
usually large as they might contain a lot of geometric data (including point
clouds and meshes). Efficient sharing of such datasets is non-trivial,
particularly when the said data is dynamically acquired (\eg in the case of
map building or object recognition).

>>>>

Difficulties however arise quickly. These different components might need
different models, at different spatial and temporal resolutions. A 3D motion
planner would typically use coarse 3D models of surrounding objects to lower the
computational load while planning, while a spatial reasoner might need on the
contrary a high-resolution model of the environment for accurate rendering when
attempting to estimate the visibility of an object. Spatial models are also
usually large as they might contain a lot of geometric data (including point
clouds and meshes). Efficient sharing of such datasets is non-trivial,
particularly when the said data are dynamically acquired (\eg in the case of
map building or object recognition).
